---
title: "Self-test and Cross-test"
author: "Chengxue Li"
date: "Last update: `r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    includes:
      in_header: header.html
editor_options: 
  markdown: 
    wrap: 72
---

## Generate OM and Perform Self- and Cross-test

This vignette includes an example of how to use the `whamMSE` (the Woods
Hole Assessment Model Management Strategy Evaluation) package to
generate an multi-stock multi-region operating model and perform
self-test and cross-test.

### 1. Load "WHAM" and "whamMSE":

```{r, eval=FALSE}
library(wham)
library(whamMSE)

main.dir = here::here()
```

### 2. Generate basic information

The operating model is generated based on user-specified biological and
fishery information. The "generate_basic_info" function is used to
create a list of biological and fishery information that are used for
generating a wham input. This function is designed for the users who
don't have an ASAP3.dat file (wham is designed to take an ASAP3.dat file
as input). Users can define the type of fish life history, lifespan,
length-at-age, weight-at-age, maturity-at-age. Users can also set fleet
information, survey information, and fishing history.

```{r, eval=FALSE}
year_start  <- 1  # starting year in the burn-in period
year_end    <- 20  # end year in the burn-in period
# Note: no need to include MSE_years in simulation-estimation 

info <- generate_basic_info(n_stocks = 2,
                            n_regions = 2,
                            n_indices = 2,
                            n_fleets = 2,
                            n_seasons = 4,
                            base.years = year_start:year_end,
                            life_history = "medium",
                            n_ages = 12,
                            fracyr_spawn = 0.625) 

basic_info = info$basic_info # collect basic information
catch_info = info$catch_info # collect fleet catch information
index_info = info$index_info # collect survey information
F_info = info$F # collect fishing information

# see more details using ?generate_basic_info
```

### 3. Configure selecitvity and natural mortality

The default for selectivity and natural mortality is constant. Modeling
selectivity and natural mortality as time and/or age varying (treated as
random effects) is optional. More details can be found in the vignettes here
(<https://timjmiller.github.io/wham/>).

```{r, eval=FALSE}
n_stocks  <- as.integer(basic_info['n_stocks'])
n_regions <- as.integer(basic_info['n_regions'])
n_fleets  <- as.integer(basic_info['n_fleets'])
n_indices <- as.integer(basic_info['n_indices'])
n_ages    <- as.integer(basic_info['n_ages'])

# Selectivity Configuration
fleet_pars <- c(5,1)
index_pars <- c(2,1)
sel <- list(model=rep("logistic",n_fleets+n_indices),
            initial_pars=c(rep(list(fleet_pars),n_fleets),rep(list(index_pars),n_indices)))

# M Configuration
M <- list(model="constant",initial_means=array(0.2, dim = c(n_stocks,n_regions,n_ages)))
```

### 4. Configure numbers-at-age (NAA)

Recruitment is assumed to vary around the mean (default), but users are
allowed to use "Beverton-Holt" or "Ricker" stock-recruitment functions.
More details can be found in the vignettes of single-wham
(<https://timjmiller.github.io/wham/>).

```{r, eval=FALSE}
sigma        <- "rec+1"
re_cor       <- "iid"
ini.opt      <- "equilibrium" # option <- c("age-specific-fe", "equilibrium")
Rec_sig      <- 0.2 # (sigma for recruitment)
NAA_sig      <- 0.1 # (sigma for NAA)

sigma_vals = array(NAA_sig, dim = c(n_stocks, n_regions, n_ages)) # input sigma for NAA
sigma_vals[,,1] = Rec_sig # input sigma for Rec

NAA_re <- list(N1_model=rep(ini.opt,n_stocks),
               sigma=rep(sigma,n_stocks),
               cor=rep(re_cor,n_stocks),
               recruit_model = 2,  # rec random around the mean
               sigma_vals = sigma_vals) # NAA_where must be specified in basic_info!
```

### 5. Generate wham input

Here we use `prepare_wham_input()` function to generate a wham input
using the basic information we set above:

```{r, eval=FALSE}
input <- prepare_wham_input(basic_info = basic_info, 
                            selectivity = sel, 
                            M = M, 
                            NAA_re = NAA_re, 
                            catch_info = catch_info, 
                            index_info = index_info, 
                            F = F_info)
```

### 6. Generate operating model

```{r, eval=FALSE}
om <- fit_wham(input, do.fit = F, do.brps = T, MakeADFun.silent = TRUE)
# Note: do.fit must be FALSE (no modeling fitting yet)
```

### 7. Self-test

Create a function to generate data and perform a self-test:

```{r, eval=FALSE}
sim_fn <- function(om, self.fit = FALSE){
  input <- om$input
  input$data <- om$simulate(complete=TRUE)
  # $simulate() is a function to generate datasets given the parameters defined in the OM
  # Note: process error and observation error are both turned on when simulating datasets 
  # To turn them off, use basic_info$simulate_process_error = 0 and basic_info$simulate_observation_error = 0
  if(self.fit) {
    fit <- fit_wham(input, do.osa = FALSE, do.retro = FALSE, MakeADFun.silent = TRUE)
    return(fit)
  } else return(input) 
}
# Note: turn on do.osa to calculate one-step-ahead residuals
# Note: turn on do.retro to calculate retrospective bias
set.seed(12345)
self_sim_fit <- sim_fn(om, self.fit = TRUE)
```

We use `check_convergence()` function to check the model convergence:

```{r, eval=FALSE}
check_convergence(self_sim_fit) # check the model convergence
```

### 8. Create HTML file to view output plots in browser (optional)

```{r, eval=FALSE}
plot_wham_output(self_sim_fit, out.type = "html")

# Create a sub directory and saves .png files (optional)

# report.dir <- "report"
# if (file.exists(main.dir, report.dir)){
# } else {
#   dir.create(file.path(main.dir, report.dir))
# }
# plot_wham_output(self_sim_fit, dir.main = file.path(main.dir, report.dir),out.type = 'png')
```

### 9 Cross-test

Different NAA configuration is used in the estimation model:

```{r, eval=FALSE}
# EM with different NAA configuration
sigma      <- "rec"
re_cor     <- "ar1" # Misspecification here
ini.opt    <- "equilibrium"

NAA_re <- list(N1_model=rep(ini.opt,n_stocks),
               sigma=rep(sigma,n_stocks),
               cor=rep(re_cor,n_stocks),
               recruit_model = 2)
               
# Generate wham input
input <- prepare_wham_input(basic_info = basic_info, 
                            selectivity = sel, 
                            M = M, 
                            NAA_re = NAA_re,
                            catch_info = catch_info, 
                            index_info = index_info, 
                            F = F_info)

# Generate EM
em <- fit_wham(input, do.fit = F, do.brps = F, MakeADFun.silent = TRUE)
```

Create a function to generate data and perform a cross-test

```{r, eval=FALSE}
sim_fn2 <- function(om, em, cross.fit = FALSE){
  input <- em$input
  input$data <- om$simulate(complete=TRUE)
  if(cross.fit) {
    fit <- fit_wham(input, do.osa = FALSE, do.retro = FALSE, MakeADFun.silent = TRUE)
    return(fit)
  } else return(input) 
}

set.seed(123)
cross_sim_fit <- sim_fn2(om, em, cross.fit = TRUE)
```

Check model convergence:

```{r, eval=FALSE}
check_convergence(cross_sim_fit) # just an example, do not expect model convergence
```

### 10. Create HTML file to view output plots in browser (optional)

```{r, eval=FALSE}
plot_wham_output(cross_sim_fit, out.type = "html")
```

### 11. Generate 100 replicates for self-tests (optional)

Parameters (including random effects parameters) associated with
population dynamics are now defined in the operating model. Users can
generate pseudo observational data from the operating model with process
and observation errors randomly drawn from their corresponding
likelihood distribution. Generating 100 pseudo data is common when
performing a self test.

```{r, eval=FALSE}
nsim <- 100 
set.seed(8675309) 
sim_input <- list()
sim_input <- lapply(1:nsim, function(x) {
  input_i <- om$input
  sim <- om$simulate(complete=TRUE)
  input_i$data <- sim
  return(input_i)
})

# Self test
sim_fits <- list()
sim_fits <- lapply(1:nsim, function(x){
  cat(paste("model_fit:", x, "start \n"))
  out <- fit_wham(sim_input[[x]], do.osa = FALSE, MakeADFun.silent = TRUE, retro.silent = TRUE, save.sdrep = FALSE)
  cat(paste("model_fit:", x, "done \n"))
  return(out)
})

# Summarize results 
conv <- sapply(1:nsim, function(x){
  if (length(sim_fits[[x]]) != 0) {
    if (sim_fits[[x]]$is_sdrep & !sim_fits[[x]]$na_sdrep & !sim_fits[[x]]$hessian) {
      conv = TRUE } else conv = FALSE
  } else conv = FALSE
  return(conv)
})
cat(paste("Convergence rate:", sum(conv)/nsim))

mean_rec_par <- lapply(1:nsim, function(x){
  mean_rec_par_est <- sim_fits[[x]]$parList$mean_rec_pars[,1]
  mean_rec_par_true <- sim_fits[[x]]$input$par$mean_rec_pars[,1]
  mean_rec_par <- cbind(mean_rec_par_est,mean_rec_par_true)
  return(mean_rec_par)
})
print(mean_rec_par)

SSB <- lapply(1:nsim, function(x){
  SSB_est <- sim_fits[[x]]$rep$SSB
  SSB_true <- sim_fits[[x]]$input$data$SSB
  SSB <- cbind(SSB_est, SSB_true)
  return(SSB)
})
print(SSB)
```

### 12. Generate 100 replicates for cross-tests (optional)

```{r, eval=FALSE}
nsim <- 100
set.seed(8675309) 
sim_input <- list()
sim_input <- lapply(1:nsim, function(x) {
  input_i <- em$input
  sim <- om$simulate(complete=TRUE)
  input_i$data <- sim
  return(input_i)
})

cross_sim_fit <- list()
cross_sim_fit <- lapply(1:nsim, function(x){
  cat(paste("model_fit:", x, "start \n"))
  out <- fit_wham(sim_input[[x]], do.osa = FALSE, MakeADFun.silent = TRUE, retro.silent = TRUE, save.sdrep = FALSE)
  cat(paste("model_fit:", x, "done \n"))
  return(out)
})
```


