---
title: "Environmental Consideration in MSE"
author: "Chengxue Li"
date: "Last update: `r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    includes:
      in_header: header.html
editor_options: 
  markdown: 
    wrap: 72
---

This vignette introduces how to incorporate environmental covariate into MSE:

### 1. Load "WHAM" and "whamMSE":

```{r, eval=FALSE}
library(wham)
library(whamMSE)

main.dir = here::here()
```

### 2. Generate basic information

```{r, eval=FALSE}

year_start  <- 1  # starting year in the burn-in period
year_end    <- 20  # end year in the burn-in period
MSE_years   <- 3     # number of years in the feedback loop
# Note: no need to include MSE_years in simulation-estimation 

info <- generate_basic_info(n_stocks = 1,
                            n_regions = 1,
                            n_indices = 1,
                            n_fleets = 1,
                            n_seasons = 1,
                            base.years = year_start:year_end,
                            n_feedback_years = MSE_years,
                            life_history = "medium",
                            n_ages = 12) 

basic_info = info$basic_info # collect basic information
catch_info = info$catch_info # collect fleet catch information
index_info = info$index_info # collect survey information
F_info = info$F # collect fishing information

```

### 3. Configure selecitvity and natural mortality

```{r, eval=FALSE}
n_stocks  <- as.integer(basic_info['n_stocks'])
n_regions <- as.integer(basic_info['n_regions'])
n_fleets  <- as.integer(basic_info['n_fleets'])
n_indices <- as.integer(basic_info['n_indices'])
n_ages    <- as.integer(basic_info['n_ages'])

# Selectivity Configuration
fleet_pars <- c(5,1)
index_pars <- c(2,1)
sel <- list(model=rep("logistic",n_fleets+n_indices),
            initial_pars=c(rep(list(fleet_pars),n_fleets),rep(list(index_pars),n_indices)))

# M Configuration
M <- list(model="constant",initial_means=array(0.2, dim = c(n_stocks,n_regions,n_ages)))
```

### 4. Configure numbers-at-age (NAA)

```{r, eval=FALSE}
sigma        <- "rec+1"
re_cor       <- "iid"
ini.opt      <- "equilibrium" 
sigma_vals   <-  array(0.5, dim = c(n_stocks, n_regions, n_ages)) # NAA sigma

NAA_re <- list(N1_model=rep(ini.opt,n_stocks),
               sigma=rep(sigma,n_stocks),
               cor=rep(re_cor,n_stocks),
               recruit_model = 2,  # rec random around the mean
               sigma_vals = sigma_vals) # NAA_where must be specified in basic_info!
```

### 5. Environmental covariate on recruitment

```{r, eval = FALSE}
# Create a ecov time series
years = basic_info$years
env.dat <- data.frame(Year = years, mean = runif(length(years), -1, 1), sigma = runif(length(years), 0, 0.2))

ecov <- list(
    label = "Ecov_x",
    mean = as.matrix(env.dat$mean),
    logsigma = as.matrix(log(env.dat$sigma)),
    year = env.dat$Year,
    use_obs = matrix(1, ncol=1, nrow=dim(env.dat)[1]), # use all obs (=1)
    process_model = "rw", # "rw" or "ar1"
    recruitment_how = matrix("controlling-lag-1-linear",1,1)) #matrix for number of stocks (1) and number of Ecovs (1)
```

### 6. Generate wham input

Here we use `prepare_wham_input()` function to generate a wham input using the basic information we set above:

```{r, eval = FALSE}
input <- prepare_wham_input(basic_info = basic_info, 
                            selectivity = sel, 
                            M = M, 
                            NAA_re = NAA_re,
                            ecov = ecov,
                            catch_info = catch_info, 
                            index_info = index_info, 
                            F = F_info)
```

### 7. Generate operating model

```{r, eval=FALSE}
random = input$random # check what processes are random effects
input$random = NULL # so inner optimization won't change simulated RE
om <- fit_wham(input, do.fit = F, do.brps = T, MakeADFun.silent = TRUE)
# Note: do.fit must be FALSE (no modeling fitting yet)
```

### 8. Generate dataset

```{r, eval=FALSE}
om_with_data <- update_om_fn(om, seed = 123, random = random)
```

### 9. Specify assessment interval and assessment year in the feedback loop

```{r, eval=FALSE}
assess.interval <- 3 # Note: assessment interval is 3 years, given the feedback period is 3 years, there will be only 1 assessment
base.years      <- year_start:year_end # Burn-in period
first.year      <- head(base.years,1)
terminal.year   <- tail(base.years,1)
assess.years    <- seq(terminal.year, tail(om$years,1)-assess.interval,by = assess.interval)
```

### 10. Use the EM same as OM to conduct MSE

```{r, eval = FALSE}
mod = loop_through_fn(om = om_with_data,
                      em_info = info, 
                      random = random,
                      M_em = M, 
                      sel_em = sel,
                      NAA_re_em = NAA_re, 
                      ecov_em = ecov,
                      age_comp_em = "multinomial",
                      em.opt = list(separate.em = FALSE, 
                                    separate.em.type = 3, 
                                    do.move = FALSE, 
                                    est.move = FALSE),
                      assess_years = assess.years, 
                      assess_interval = assess.interval, 
                      base_years = base.years,
                      year.use = 20,
                      add.years = TRUE, 
                      seed = 123,
                      save.sdrep = TRUE,
                      save.last.em = TRUE)
```

